Adolescent well-being in the digital age

### 2022-03-24 00-clean.Rmd
Use synthpop for mock data

-   Clean the variable names
-   Set appropriate missing values (`NaN`, not e.g. `-99`)
-   Use appropriate coding schemes (e.g. 0: no; 1: yes)
-   Calculate scale scores (means over items)
-   Rescale outcomes to proportions (0 - 1)
-   Subset the data to 15 to 24 year olds
-   Create age-categories in line with GBD data
-   Drop one 13 year old as this data should only have people 15 and older

@@

gwp <- gwp %>%
  clean_names() %>%
  transmute(
    country = countrynew,
    year = year_calendar,
    id = wpid,
    sex = factor(wp1219, levels = c(2, 1), labels = c("Female", "Male")),
    age = wp1220,
    # Don't know, refused, and missing values
    Life_satisfaction = if_else(between(wp16, 0, 10), wp16, NaN),
    across(wp60:wp74, ~ if_else(between(., 1, 2), ., NaN)),
    # Also reverse the weird 1: yes 2: no coding here
    across(wp60:wp74, ~ 3 - .)
  )

@@

We then load the synthetic GWP dataset if the real data was not found. This is just a list of the countries, years and demographics in the actual data, with gaussian noise for the outcomes' mean and SE values.

```{r}
# Create if doesn't exist
gwp_mock_path <- "data-raw/gwp-MOCK.rds"
if (!file.exists(gwp_mock_path)) {
  set.seed(101010)
  # TODO
}
# Load if actual data doesn't exist
if (!dir.exists("data-raw/Gallup")) {
  cat("Using synthetic GWP data.")
  gwp <- read_rds(gwp_mock_path)
} else {
  cat("Using actual GWP data.")
}
```

@@

# Transform internet edge cases
itu <- itu %>%
  mutate(internet = if_else(internet == 0, .0000001, internet)) %>%
  mutate(internet = if_else(internet == 1, .9999999, internet)) %>% 
  mutate(mobile = if_else(mobile == 0, .0000001, mobile)) %>%
  mutate(mobile = if_else(mobile == 1, .9999999, mobile))

>>>>

-   Clean the variable names
-   Set appropriate missing values (`NaN`, not e.g. `-99`)
-   Use appropriate coding schemes (e.g. 0: no; 1: yes)
-   Calculate scale scores (means over items)
-   Rescale outcomes to proportions (0 - 1)
-   Create age categories in line with GBD data
-   Drop one 13 year old as this data should only have people 15 and older
-   Exclude people older than 89

@@

# Rename and recode variables
gwp <- gwp %>%
  clean_names() %>%
  transmute(
    country = countrynew,
    year = year_calendar,
    id = wpid,
    sex = factor(wp1219, levels = c(2, 1), labels = c("Female", "Male")),
    age = wp1220,
    # Don't know, refused, and missing values
    Life_satisfaction = if_else(between(wp16, 0, 10), wp16, NaN),
    across(wp60:wp74, ~ if_else(between(., 1, 2), ., NaN)),
    # Also reverse the weird 1: yes 2: no coding here
    across(wp60:wp74, ~ 3 - .)
  )

@@

### Synthetic GWP data

If the real GWP data was not available above, here we load the synthetic dataset (having first created it).

```{r create-mock-gwp-data}
#| eval: false
gwp_mock_path <- "data-raw/gwp-MOCK.rds"
library(synthpop)
gwp_syn <- gwp %>% 
  drop_na()
gwp_syn <- syn(
  gwp_syn %>% filter(outcome == "Life_satisfaction"), 
  method = c("", "", "", "", "", "normrank", "normrank"),
  # visit.sequence = c(1:6, 8, 7),
  maxfaclevels = 168
  )
saveRDS(gwp_syn, gwp_mock_path)
```

```{r}
gwp_mock_path <- "data-raw/gwp-MOCK.rds"
# Load if actual data doesn't exist
if (!dir.exists("data-raw/Gallup")) {
  cat("Using synthetic GWP data.")
  gwp <- read_rds(gwp_mock_path)
} else {
  cat("Using actual GWP data.")
}
```

@@

# Transform internet edge cases
itu <- itu %>%
  mutate(internet = if_else(internet == 0, .0000001, internet)) %>%
  mutate(internet = if_else(internet == 1, .9999999, internet))
